---
TEMPLATE: template.html
DESTINATION: ../index.html
BROWSERTITLE: YODA
SITETITLE: Yale Order of Data Analysts
SITESUBTITLE: YODA
MENU: About Us;.,Minutes;minutes.html
PAGETITLE: About Us
DATE: Updated 2013-09-24
---

### YODA our name is!

The Yale Order of Data Analysts was founded on Tuesday, September 3, 2013, by (listed alphabetically) Stephanie Adcock, Jessica Allen, Rosie Buchanan, Henry Davidge, Sarah Ditchek, Jay Emerson, Gaby Garbasz, Jessica Landau-Taylor, Pranav Maddi, Dan Noble, John Park, Kishen Patel,  Tammy Pham, Sharon Qian, and Jacob Rosenberg-Wohl.

### YODA meetings

YODA meets on Tuesday evenings at 8 PM in the TEAL classroom of 27 Hillhouse Avenue.
[Obi wan](http://www.stat.yale.edu/~jay/)
will often bring food and drink.  Come and go as you please and as time permits!

### Planning for YODA 10/8

We'll do something data-related, or else perhaps a Google Code Jam
problem.  All are welcome!


### A basic code chunk example

```{r}
set.seed(1)
x <- rnorm(10)
summary(x)
```

### I can even get plots to work!

```{r}
hist(x)
```

### Minutes of past meetings of YODA

We archive basic minutes from [past meetings](minutes.html).
